---
title: 'DA5020 - Project Sentimental Analysis on Amazon Reviews'
date: '`r Sys.Date()`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  # mute messages output
  message = FALSE,warning=FALSE
)
```

# Libraries used
```{r}
library(rvest)
library(dplyr)
library(tidyverse)
library(stringr)
library(tibble)
library(RSQLite)
library(sentimentr)
library(dplyr)
library(stringr)
library(tidytext)
library(wordcloud)
library(reshape2)



```

#Reviews data function for one page
```{r}
product<-function(keyword,page)
{
  url<-"https://www.amazon.com/product-reviews/%s/ref=cm_cr_arp_d_paging_btm_%i?ie=UTF8&reviewerType=all_reviews&pageNumber=%i"
  amazon<-sprintf(url,URLencode(keyword),page,page)
  reviewpage<-read_html(amazon)
  
  
  
  profile_name <- reviewpage%>%
    html_nodes(".review-byline .author")%>%
    html_text(trim=T)%>%
    gsub("By","",.)
  
  
  personal_rating <- reviewpage%>%
    html_nodes("#cm_cr-review_list  .review-rating")%>%
    html_text()%>%
    str_extract("\\d")%>%
    as.numeric()
  
  
  description <- reviewpage%>%
    html_nodes("#cm_cr-review_list .a-color-base")%>%
    html_text(trim=T)
  
  
  review <- reviewpage%>%
    html_nodes(".review-text")%>%
    html_text(trim=T)
  
  
  verification <- reviewpage%>%
    html_nodes(".review-data.a-spacing-mini")%>%
    html_text(trim=T)%>%
    grepl("Verified Purchase",.)
  
  product_id<-keyword
  df <- data.frame(profile_name,personal_rating,description,review,verification,product_id)
  
  
}
product("B0756CYWWD",4)

```


# Database for both the tables

```{r}
ma<-dbConnect(SQLite(),dbname="x.sqlite")


dbSendQuery(conn=ma,"create table maintable(
            product_id1 text primary key,
            name1 text,
            price1 num,
            ratings1 num,
            no_of_reviews1 num)
            without rowid")
dbSendQuery(conn=ma,"create table reviewtable(
            profile_name text,
            personal_rating num,
            description text,
            review text,
            verification logical,
            product_id1 text,
            foreign key(product_id1) references maintable(product_id1))")

```

# Multiple page of reviews data
```{r}
multiple_page <- function(keyword,page)
{
  x <- map(1:page,function(n)
  {
    product(keyword,n)
  })%>%
    bind_rows()
  dbWriteTable(conn=ma,name="reviewtable",value=x,row.names=F,header=T,overwrite=T)
  
}

multiple_page("B0756CYWWD",4)

```





#main page function
```{r}
main_page <- function(keyword)
{
  main <- "https://www.amazon.com/gp/product/%s"
  item <- sprintf(main,URLencode(keyword))
  items <- read_html(item)
  name <- items%>%
    html_node("#productTitle")%>%
    html_text(trim=T)
  
  ratings <- items%>%
    html_node(".arp-rating-out-of-text")%>%
    html_text()%>%
    str_extract("\\d{1}.\\d{1}")%>%
    as.numeric()
  
  price <- items%>%
    html_node("#priceblock_ourprice")%>%
    html_text(trim=T)%>%
    gsub("\\$","",.)%>%
    as.numeric()
  
  no_of_reviews <- items%>%
    html_node("#acrCustomerReviewText")%>%
    html_text(trim=T)%>%
    gsub("[A-z]","",.)%>%
    gsub(",","",.)%>%
    as.numeric()
  
  product_id <- keyword
  
  df <- data_frame(product_id,name,price,ratings,no_of_reviews)
  
  dbWriteTable(conn=ma,name="maintable",value=df,row.names=F,header=T,overwrite=T)
  
}
main_page("B0756CYWWD")

```

# All the data of the product including reviews and basic details
```{r}
a<-dbGetQuery(conn=ma,"select * from maintable m
              join reviewtable r
              on m.product_id=r.product_id")
head(a)

```

# Sentiment_by used to show the average sentimental score of each review
```{r}
sent_agg <- with(a, sentiment_by(review))
head(sent_agg)

```

# Plot showing the difference between personal rating and average _sentiment
```{r}
par(mfrow=c(1,2))
with(a, hist(personal_rating))
with(sent_agg, hist(ave_sentiment))

```

# Difference in the mean
```{r}
mean(a$personal_rating)
mean(sent_agg$ave_sentiment)

```

# Good reviews and bad reviews highlighted in the text
```{r}
best_reviews <- slice(a, top_n(sent_agg, 10, ave_sentiment)$element_id)
with(best_reviews, sentiment_by(review)) %>% highlight()

worst_reviews <- slice(a, top_n(sent_agg, 10, -ave_sentiment)$element_id)
with(worst_reviews, sentiment_by(review)) %>% highlight()

```

# Word count of all the reviews combined
```{r}
b<-a$review
text_tb <- tibble(c = seq_along(b),
                  text = b)
x<-text_tb %>%
  unnest_tokens(word, text)
x%>%
  count(word,sort=T)
```

# Stopwords or words that do not make sense are removed
```{r}
x %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)

```

# Words are categorized into basic words
```{r}
x %>%
  right_join(get_sentiments("nrc")) %>%
  filter(!is.na(sentiment)) %>%
  count(sentiment, sort = TRUE)

```

# plot showing the word frequency in both negative and positive comments 
```{r}

bing_word_counts <- x %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ggplot(aes(reorder(word, n), n, fill = sentiment)) +
  geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment", x = NULL) +
  coord_flip()

```

# Wordcloud show the frequency of words
```{r}
x %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))

```

# Wordcloud showing the frequency based on the size and also whether it is positive or negative based on color
```{r}
x %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("#F8766D", "#00BFC4"),
                   max.words = 100)


```


